---
output: github_document
editor_options: 
  chunk_output_type: console
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# findpeaks

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
<!-- badges: end -->

The goal of findpeaks is finding maxima in fluorescence profile generated from microscopic time-lapse movie of Streptomyces.

Online version of the app can be found [here](http://microbesinwroclaw.biotech.uni.wroc.pl:3838/zmm_apps/findpeaks/).

## Installation

You can install the released version of findpeaks from Github, but first other R packages should be installed:

For running the app package Peaks is required. It can be installed on linux using:

``` r
devtools::install_version('Peaks', version = '0.2', repos = "http://cran.us.r-project.org")
```
Windows users first have to install [Rtools 4.0.0](https://cran.r-project.org/bin/windows/Rtools/), which is necessary for package compilation from source, and then install package Peaks as above. 

Package EBImage can be installed from bioconductor:

``` r

if (!requireNamespace("BiocManager", quietly = TRUE))
    install.packages("BiocManager")
BiocManager::install(version = "3.11")
BiocManager::install("EBImage")

```

Then you should be able to install and run package findpeaks:

``` r
devtools::install_github('astrzalka/findpeaks')

findpeaks::run_app()
```



Peak detection uses R package Peaks. Please cite:

```{r echo=FALSE}

print(citation("Peaks"), bibtex = F)

```


Fluorescence profiles data can be prepared using an ImageJ script: imagej_get_profile.ijm , which will save the profiles for all selected ROIs for each channel separately. It will also save ROIs and duplicated tiff file of analyzed hypha in the same directory. 

All analysis and plotting functions can be also used outside of shiny application as shown in the example below:


```{r}

data <- findpeaks::dane_2

result <- findpeaks::find_peaks(data, s = 2.5, m = FALSE, procent = 0.4, threshold = 41)

findpeaks::plot_find_peaks(dane_raw = result[[2]], result[[1]])

#sometimes unwamted complexes can be removed manually

result[[1]] <- result[[1]][-c(4),]

```

Result of the find_peaks function is a list, where the first data frame is the localization and fluorescence intensity of each found maximum and second data frame contains a smoothed fluorescence profile for each time point.

```{r}
head(result[[1]])

head(result[[2]])
```


Alternatively complexes localizations can be visualized as a kymograph or a hypha scheme  

```{r}

findpeaks::plot_kymograph_find_peaks(dane_raw = data, dane_find = result[[1]], color_point = 'red', color_gradient = 'green3', lapse = 10, odwroc = FALSE)

findpeaks::plot_scheme_find_peaks(dane_find = result[[1]], odwroc = FALSE)

```


FLuorescence profiles can also be plotted as ridges plot:


```{r}
findpeaks::plot_peaks_ridges(data = data)
```

